### 2018-05-04 paper/3-abstractions.tex
Fix paper build

\subsection{Common vocabulary for build systems}\label{sec-vocabulary}
\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- An abstract store
data Store i k v
getInfo    :: Store i k v -> i
putInfo    :: i -> Store i k v -> Store i k v
getValue   :: k -> Store i k v -> v
putValue   :: Eq k => k -> v -> Store i k v -> Store i k v
getHash    :: Hashable v => k -> Store i k v -> Hash v
initialise :: i -> (k -> v) -> Store i k v
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Hashing
hash :: Hashable a => a -> Hash a
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Applicative functors
pure  :: Applicative f => a -> f a
(<$>) :: Applicative f =>   (a -> b) -> f a -> f b -- Left-associative
(<*>) :: Applicative f => f (a -> b) -> f a -> f b -- Left-associative
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Standard State monad from Control.Monad.State
data State s a
instance Applicative (State s)
instance Monad       (State s)
get       :: State s s
gets      :: (s -> a) -> State s a
modify    :: (s -> s) -> State s ()
execState :: State s a -> s -> s
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Standard types from Data.Functor.Identity and Data.Functor.Const
newtype Identity a = Identity { runIdentity :: a }
newtype Const m a  = Const    { getConst    :: m }
\end{minted}
\vspace{0.5mm}
\begin{minted}[fontsize=\small]{haskell}
instance Functor (Const m) where
    fmap _ (Const m) = Const m
\end{minted}
\vspace{0.5mm}
\begin{minted}[fontsize=\small]{haskell}
instance Monoid m => Applicative (Const m) where
    pure _              = Const mempty
    Const x <*> Const y = Const (x <> y)
\end{minted}
\vspace{-3mm}
\caption{Signatures of main data types and library functions.}\label{fig-types}
\vspace{-4mm}
\end{figure}
We begin by establishing a common vocabulary for build systems:

>>>>

\subsection{Common vocabulary for build systems}\label{sec-vocabulary}
\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- An abstract store
data Store i k v -- i = info, k = key, v = value
getInfo    :: Store i k v -> i
putInfo    :: i -> Store i k v -> Store i k v
getValue   :: k -> Store i k v -> v
putValue   :: Eq k => k -> v -> Store i k v -> Store i k v
getHash    :: Hashable v => k -> Store i k v -> Hash v
initialise :: i -> (k -> v) -> Store i k v
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Hashing
hash :: Hashable a => a -> Hash a
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Applicative functors
pure  :: Applicative f => a -> f a
(<$>) :: Applicative f =>   (a -> b) -> f a -> f b -- Left-associative
(<*>) :: Applicative f => f (a -> b) -> f a -> f b -- Left-associative
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Standard State monad from Control.Monad.State
data State s a
instance Applicative (State s)
instance Monad       (State s)
get       :: State s s
gets      :: (s -> a) -> State s a
modify    :: (s -> s) -> State s ()
execState :: State s a -> s -> s
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Standard types from Data.Functor.Identity and Data.Functor.Const
newtype Identity a = Identity { runIdentity :: a }
newtype Const m a  = Const    { getConst    :: m }
\end{minted}
\vspace{0.5mm}
\begin{minted}[fontsize=\small]{haskell}
instance Functor (Const m) where
    fmap _ (Const m) = Const m
\end{minted}
\vspace{0.5mm}
\begin{minted}[fontsize=\small]{haskell}
instance Monoid m => Applicative (Const m) where
    pure _              = Const mempty
    Const x <*> Const y = Const (x <> y)
\end{minted}
\vspace{-3mm}
\caption{Signatures of main data types and library functions.}\label{fig-types}
\vspace{-4mm}
\end{figure}
We begin by establishing a common vocabulary for build systems:
